WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-17 paper/Manuscript_DS.Rmd
Fix reference to FOSTER definition

Although open science is advocated by many,
it does not have a unitary definition.
Throughout this paper, we adhere to the definition of open science as
"the practice of science in such a way that others can collaborate and contribute,
where research data, lab notes and other research processes are freely available,
under terms that enable reuse, redistribution and reproduction of the research and its underlying data and methods" [@vicente-saezOpenScienceNow2018].
In this definition, the term "science" refers to all scholarly disciplines.
We further define the term *reproducible*, as used in the WORCS acronym, as being able to re-perform "the same analysis with the same code using a different analyst" [@patilVisualToolDefining2019].

>>>>

Although open science is advocated by many,
it does not have a unitary definition.
Throughout this paper, we adhere to the definition of open science as
"the practice of science in such a way that others can collaborate and contribute,
where research data, lab notes and other research processes are freely available,
under terms that enable reuse, redistribution and reproduction of the research and its underlying data and methods" [the [FOSTER Open Science Definition](https://www.fosteropenscience.eu/foster-taxonomy/open-science-definition), as discussed in @sonjabezjakOpenScienceTraining2018].
In this context, the term "science" refers to all scholarly disciplines.
We further define the term *reproducible*, as used in the WORCS acronym, as being able to re-perform "the same analysis with the same code using a different analyst" [@patilVisualToolDefining2019].
